---
title       : Forecasting Australian wine sales
subtitle    : Using the forecast and shiny packages
author      : rquadrat
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Data Description

* The data is included in the R forecast package
* Data can be found at [datamarket.com](https://datamarket.com/data/set/22q2/monthly-australian-wine-sales-thousands-of-litres-by-wine-makers-in-bottles-1-litre)
* It contains Australian total wine sales by wine makers in bottles smaller and equal to 1 litre
* Data is from January 1980 to August 1994

The first few entries (in thousand litres) are:
```{r, echo=F, message=F}
options(width=78)
require(forecast)
data("wineind")

window(wineind, 1980, 1982.99)

```


---

## Applied model

The Goal is the forecast of future wine sales in Australia. 
A special class of time series modelling functions is applied: 
A non-seasonal ARIMA model is defined by:
$$ y'_{t} = c + \phi_{1}y'_{t-1} + \cdots + \phi_{p}y'_{t-p} + \theta_{1}e_{t-1} + \cdots + \theta_{q}e_{t-q} + e_{t}$$
The degrees of the ARIMA model are determined with the forecast::auto.arima() function. The best model is selected based on the AICc criterium (The lower the better)
```{r, echo=1:2}

model<-auto.arima(wineind, max.order=6, stepwise=T, approximation = T)
{
print("Coefficients of model:")
print(model$coef)
}

```

---

## The shiny application
* Allows

---

## Further Improvements

* Other model as ets or tbats can be used for comparison
* a dataset could be made selective 
* include testset for forecast quality validation
